О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-16 pps-linear-bound/pps-linear-lower-bound.tex
Advices to language issues list
Proper acknowledgements to Dr. Usachev

		is it correct to split the sentence in such a way?

	\item
		For the sake of completeness.

		Is the phrase correct?
		There should be an example in one of papers about Banach limits...

@@

	\item
		Observation vs. Proposition

@@

\section{Acknowledgements}
Author thanks Prof. E.M. Semenov for the fruitful discussion and ideas
and A.S. Chervinskaia for the idea of using the term ``facher'' and other linguistic advices.

>>>>

		is it correct to split the sentence in such a way?
		We should avoid it if possible.

@@

	\item
		Observation -> Proposition

@@

\section{Acknowledgements}
Author thanks Dr. Prof. E.M. Semenov for the fruitful discussion and ideas,
A.S. Chervinskaia for the idea of using the term ``facher'' and other linguistic advices,
and Dr. A.S. Usachev for proofreading.
